\vspace{-1in}Identity signaling model progress

### 2020-02-14 reports/Progress-2-14-20.tex
disliking-homoph conf exp done; on to co-evo of sig/rec strat

\title{Identity signaling model progress}

@@

\section*{Preliminary results}

For these preliminary results I focus on the evolution of signaling strategies,
and set receiving strategies to be randomly assigned with probability 0.5 to
each agent at model initialization. I set $R=0.5$, $s=0.25$, $d=\delta=0.25$,
and $N=100$. After signaling, agents go through 10 rounds of assortment/interaction,
followed by evolution after the 10 rounds of interaction. The model has been
run out to 100 timesteps where timeseries are nearly stable, though we will
want more timesteps for our final study, or perhaps adjust the number of 
assortment/interaction rounds up or down per timestep, to guarantee full 
stability (see Figure~\ref{fig:exampleSeries}).

@@

@@

Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
homophily, $w$. The bonus payoff for two interacting agents where at least one
likes the other is set to $s=0.25$. The payoff structure is as follows

\begin{table}[h]
  \centering
  \begin{tabular}{rl}
   Attitude combo. & Payoff \\
   \toprule
    Like/like & $1 + s$ \\
    Like/neutral & $1 + s$ \\
    Neutral/neutral & 1 \\
    Like/dislike & $1 + s - d$ \\
    Dislike/neutral & $1 - d$ \\
    Dislike/dislike & $1 - d - \delta$
  \end{tabular}
\end{table}

Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}
As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.
In this experiment we ran the simulations to 200 timesteps 
(Figure~\ref{fig:dislikingHomophilySeries}).

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/exampleMidrangeSeries.pdf}
  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsReceptivityHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}

>>>>

\title{\vspace{-1in}Identity signaling model progress}

@@

\section*{Evolution in signaling strategy}

For these preliminary results I focus on the evolution of signaling strategies,
and set receiving strategies to be randomly assigned with probability 0.5 to
each agent at model initialization. The output measure in these experiments
is density of covert signalers. There are confirmatory results for two
computational experiments in which I: (1) varied relative covert receptivity $r/R$ and 
homophily, $w$; and (2) varied the disliking penalties set equal, $d=\delta$,
and homophily, $w$.

@@

Here I set $R=0.5$, $s=0.25$, $d=\delta=0.25$,
and $N=100$. After signaling, agents go through 10 rounds of assortment/interaction,
followed by evolution after the 10 rounds of interaction. The model has been
run out to 100 timesteps where timeseries are nearly stable, though we will
want more timesteps for our final study, or perhaps adjust the number of 
assortment/interaction rounds up or down per timestep, to guarantee full 
stability.

@@

Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
homophily, $w$. I ran the model to 200 timesteps this time, which did allow
the series to settle more, but perhaps not to a significant degree 
(Figure~\ref{fig:dislikingHomophilySeries}). The bonus payoff for two 
interacting agents where at least one
likes the other is set fixed to $s=0.25$. The payoff structure is as follows

\begin{table}[H]
  \centering
  \begin{tabular}{rl}
   Attitude combo. & Payoff \\
   \toprule
    Like/like & $1 + s$ \\
    Like/neutral & $1 + s$ \\
    Neutral/neutral & 1 \\
    Like/dislike & $1 + s - d$ \\
    Dislike/neutral & $1 - d$ \\
    Dislike/dislike & $1 - d - \delta$
  \end{tabular}
\end{table}

Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/dislikingHomophilySeries.pdf}
  \caption{Timeseries of nine combinations of $d=\delta$ and $w$.}
  \label{fig:dislikingHomophilySeries}
\end{figure}

\begin{figure}[H]
  \centering
\includegraphics[width=0.8\textwidth]{Figures/covertDensityVsDislikingHomophily.pdf}
  \caption{Density of covert signalers at $t=100$, final timestep recorded
    in this preliminary experiment.}
  \label{fig:dislikingHomophilyHeatmap}
\end{figure}
